Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-11-26 Ben_Manuscripts/stochastic_transport/Draft.tex
Updated figure designs to help readers

  %BJC4: better visualization scheme
  %BJC4: maybe color code background based on whether its in the pore or tails
  % and then make some kind of code for trapping mechanisms. t - tails, p -
  % pores, a - associated, h - hbonded. Replace state numbers with codes). For
  % example, state 4 would be t-a-h
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  %BJC4: add Brownian limit to this? 
  \includegraphics[width=\textwidth]{H_v_state.pdf}
  \caption{}\label{fig:H_v_state}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
  \caption{}\label{fig:sigma_v_state}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{alpha_v_state.pdf}
  \caption{}\label{fig:alpha_v_state}
  \end{subfigure}
  %BJC4: I combined the following bar chart with the parameters. Let me know if that makes things less coherent.
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{state_probabilities.pdf}
  \caption{}\label{fig:state_probabilities}
  \end{subfigure}
	  \caption{The parameters of the MSDDM are strong functions of the
	  trapping mechanisms. We observe differnt parameters but with similar
	  trends between the tail and pore region. (a) Motion is highly
	  anti-correlated in trapped states. As the number of simulataneously
	  influencing trapping mechanisms increases, the hurst parameter
	  decreases. The hurst parameter is highest during transitions between
	  states (state T). (b) As more trapping mechanism simultaneously
	  influence solutes, the width of the hop length distribution
	  decreases. The largest hops occur when solutes are unbound in the
	  pores. (c) The weight of the hop length distribution's tails,
	  parameterized by $\alpha_h$ increases as more trapping mechanism
	  influence solutes simultaenously. The transition hop distributions
	  have some of the heaviest tails. (d) Solutes spend varying amounts of
	  time under the influence of each trapping mechanism. There is less
	  confidence in the parameters of states that are visited infrequently.
	  }\label{fig:msddm_parameters}
  \end{figure}

>>>>

  %BJC4: better visualization scheme
  %BJC4: maybe color code background based on whether its in the pore or tails
  % and then make some kind of code for trapping mechanisms. t - tails, p -
  % pores, a - associated, h - hbonded. Replace state numbers with codes). For
  % example, state 4 would be t-a-h
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  %BJC4: add Brownian limit to this? 
  \includegraphics[width=\textwidth]{H_v_state.pdf}
  \caption{}\label{fig:H_v_state}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
  \caption{}\label{fig:sigma_v_state}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{alpha_v_state.pdf}
  \caption{}\label{fig:alpha_v_state}
  \end{subfigure}
  %BJC4: I combined the following bar chart with the parameters. Let me know if that makes things less coherent.
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{state_probabilities.pdf}
  \caption{}\label{fig:state_probabilities}
  \end{subfigure}
	  \caption{The parameters of the MSDDM are strong functions of the
	  trapping mechanisms. We observe different parameters but with similar
	  trends between the tail and pore region. The states are defined in
	  Table~\ref{table:states}. To aid the reader, we labeled each state
	  with an abbreviation which identifies the combination of conditions
	  to which each solute is subject: t - tails, p - pores, h - hydrogen
	  bonded, a - associated with sodium. The legend in (a) applies to all
	  subplots. (a) Motion is highly anti-correlated in trapped states. As
	  the number of simulataneously influencing trapping mechanisms
	  increases, the hurst parameter decreases. The hurst parameter is
	  highest during transitions between states (state T). (b) As more
	  trapping mechanism simultaneously influence solutes, the width of the
	  hop length distribution decreases. The largest hops occur when
	  solutes are unbound in the pores. (c) The weight of the hop length
	  distribution's tails, parameterized by $\alpha_h$ increases as more
	  trapping mechanism influence solutes simultaenously. The transition
	  hop distributions have some of the heaviest tails. (d) Solutes spend
	  varying amounts of time under the influence of each trapping
	  mechanism. There is less confidence in the parameters of states that
	  are visited infrequently.
	  }\label{fig:msddm_parameters}
  \end{figure}
